### 2016-08-29 Chapters/ContributionsSummary.tex
Save the day's work

This final Chapter provides a brief overview of the motivations, results and
conclusions of the papers this thesis is based on.
All publications included in this thesis have involved some programming effort.
I will also describe the principles we have striven to follow in developing our
\acs{PCM} software library and its management philosophy.
I will also give some details on the interfaces we have developed to different
quantum chemistry codes.
Finally, for each paper, I will give a description of my contributions to the
work leading to its publication.
\todo[inline]{Write something along these lines: "My coauthors have all read and approved."}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Software}
\section*{Software}

\todo[inline]{Have a closer look at this. I think it needs to be updated for the discussion
on open-source software that went down on JPC Lett. some time ago.
Also, acronyms should be properly set up.}

A shorter version of this discussion has been accepted for publication in the
proceedings of the \emph{Producing High Performance and Sustainable Software
for Molecular Simulation} workshop held at the 2015 Supercomputing Conference.

\begin{figure}[!htb]
\centering
\includegraphics[width=.8\textwidth]{notpretty.png}
\end{figure}

@@

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=.5\textwidth]{pcmsolver-scheme}
\end{figure}

@@

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Continuum solvation in the relativistic regime}
\section*{Paper I. Continuum solvation in the relativistic regime}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{The wavelet Galerkin boundary element method for PCM}
\section*{Paper II. The wavelet Galerkin boundary element method for PCM}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Non homogeneous environments}
\section*{Paper III: Non homogeneous environments}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Relativistic Calculation of EPR and pNMR Parameters in Solution}
\section*{Paper IV: Relativistic Calculation of EPR and pNMR Parameters in Solution}

@@

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Open-ended self-consistent field response theory in solution}
\section*{Paper V: Open-ended self-consistent field response theory in solution}

>>>>

This final Chapter provides a brief overview of the motivations, results and
conclusions of the papers this thesis is based on.
All publications included in this thesis have involved some programming effort.
In Section \ref{sec:software} I will describe the principles we have
striven to follow in developing our \acs{PCM} software library and its
management philosophy.
I will also give some details on the interfaces we have developed to different
quantum chemistry codes.
A shorter version of the material in Section \ref{sec:software} has been
accepted for publication in the proceedings of the \emph{Producing High
Performance and Sustainable Software for Molecular Simulation} workshop
held at the 2015 Supercomputing Conference.~\autocite{SC15}
Sections \ref{sec:relapcm}--\ref{sec:pcmopenrsp} contain very short
summaries of the papers and a list of my contributions.
My coauthors have all read and approved the description of contributions.

@@

\section{Software}\label{sec:software}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Boost\autocite{boost}
Eigen\autocite{eigen}
libgetkw\autocite{libgetkw}
libtaylor\autocite{libtaylor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[tb]
  \centering
  \scalebox{0.8}{\input{gfx/pcmsolver-scheme.tikz}}
  \caption[Schematic view of the relationship between a host quantum chemistry
  program and the \pcmsolver library.]{
  Schematic view of the relationship between a host quantum chemistry
  program and the \pcmsolver library.
  }
\end{figure}

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=.8\textwidth]{pcmsolver-internals.png}
  \caption[Internal structure of \pcmsolver.]
  {
  Internal structure of \pcmsolver. In the grey boxes the external
  projects the library depends on.
  }
\end{figure}

@@

\section{Continuum solvation in the relativistic regime}\label{sec:relapcm}

@@

\section{The Wavelet Galerkin Boundary Element Method for PCM}\label{sec:wemlin}

@@

\section{Non homogeneous environments}\label{sec:spherical}

@@

\section{Relativistic Calculation of EPR and pNMR Parameters in
Solution}\label{sec:pcmepr}

@@

\section{Open-ended self-consistent field response theory in
solution}\label{sec:pcmopenrsp}

### 2016-08-29 FrontBackmatter/Introduction.tex
Contributions written
Save the day's work

\epigraph{
[...] og fordi jeg alltid har hatt en dragning mot det skjulte og hemmelige.
    }{
    --- \textsc{K. O. Knausgård}, \textit{Om Høsten}}

@@

\begin{figure}[tb]
\missingfigure{Add picture with multiscale models}
\caption{From quantum mechanical models to multiscale models.}
\label{fig:qm-to-multiscale}
\end{figure}

>>>>

\epigraph{
[...] \textnorsk{og fordi jeg alltid har hatt en dragning mot det skjulte og hemmelige.}
}{
--- \textnorsk{\textsc{K. O. Knausgård}, \textit{Om Høsten}}}

@@

\begin{figure}[tb]
\missingfigure{Add picture with multiscale models}
\caption[From quantum mechanical to multiscale models]{
From quantum mechanical to multiscale models.
The images used in the scheme are reproduced courtesy of Dr.~Stefano
Caprasecca (MoLEcoLab, Università di Pisa).}
\label{fig:qm-to-multiscale}
\end{figure}

### 2016-08-29 FrontBackmatter/Publications.tex
Work on the summary of papers
Save the day's work

\item
  \textbf{R. Di Remigio}, R. Bast, L. Frediani, and T. Saue
  \\
  Four-Component Relativistic Calculations in Solution with the
  Polarizable Continuum Model of Solvation: Theory,
  Implementation, and Application to the Group 16 Dihydrides
  \ce{H2X} (\ce{X} = \ce{O}, \ce{S}, \ce{Se}, \ce{Te},
  \ce{Po})
  \\
\textit{J. Phys. Chem. A}, \textrm{2015}, \textbf{119}, 5061--5077
\label{relapcm}

\item
  M. Bugeanu, \textbf{R. Di Remigio}, K. Mozgawa, S. S. Reine, H.
  Harbrecht,  and L. Frediani
  \\
  Wavelet Formulation of the Polarizable Continuum Model. II. Use of
  Piecewise Bilinear Boundary Elements
  \\
  \textit{Phys. Chem. Chem. Phys.}, \textrm{2015}, \textbf{17},
  31566--31581
\label{wemlin}

\item
  \textbf{R. Di Remigio}, K. Mozgawa, H. Cao, V. Weijo, and L.
  Frediani
  \\
  A Polarizable Continuum Model for Molecules at Spherical
  Diffuse Interfaces
  \\
  \textit{J. Chem. Phys.}, \textrm{2016}, \textbf{144}, 124103
\label{spherical}

\item
  \textbf{R. Di Remigio}, M. Repisky, S. Komorovsky, P. Hrobarik, L.
  Frediani, and K. Ruud
  \\
  Four-Component Relativistic Density Functional Theory with the
  Polarizable Continuum Model: Application to EPR Parameters
  and Paramagnetic NMR Shifts
  \\
  submitted for publication to \textit{Mol. Phys.}
\label{pcmepr}

\item
  \textbf{R. Di Remigio}, M. T. P. Beerepoot, Y. Cornaton, M. Ringholm,
  A. H. S. Steindal, K. Ruud, and L. Frediani
  \\
  Open-ended formulation of self-consistent field response theory with
  the polarizable continuum model for solvation
  \\
  In preparation for submission to \textit{Phys. Chem. Chem. Phys.}
\label{pcmopenrsp}
\end{enumerate}

>>>>

\item
  \textbf{R. Di Remigio}, R. Bast, L. Frediani, and T. Saue
  \\
  \textsc{
  Four-Component Relativistic Calculations in Solution with the
  Polarizable Continuum Model of Solvation: Theory,
  Implementation, and Application to the Group 16 Dihydrides
  \ce{H2X} (\ce{X} = \ce{O}, \ce{S}, \ce{Se}, \ce{Te},
  \ce{Po})
  }
  \\
\textit{J. Phys. Chem. A}, \textrm{2015}, \textbf{119}, 5061--5077
\label{relapcm}

\item
  M. Bugeanu, \textbf{R. Di Remigio}, K. Mozgawa, S. S. Reine, H.
  Harbrecht,  and L. Frediani
  \\
  \textsc{
  Wavelet Formulation of the Polarizable Continuum Model. II. Use of
  Piecewise Bilinear Boundary Elements
  }
  \\
  \textit{Phys. Chem. Chem. Phys.}, \textrm{2015}, \textbf{17},
  31566--31581
\label{wemlin}

\item
  \textbf{R. Di Remigio}, K. Mozgawa, H. Cao, V. Weijo, and L.
  Frediani
  \\
  \textsc{
  A Polarizable Continuum Model for Molecules at Spherical
  Diffuse Interfaces
  }
  \\
  \textit{J. Chem. Phys.}, \textrm{2016}, \textbf{144}, 124103
\label{spherical}

\item
  \textbf{R. Di Remigio}, M. Repisky, S. Komorovsky, P. Hrobarik, L.
  Frediani, and K. Ruud
  \\
  \textsc{
  Four-Component Relativistic Density Functional Theory with the
  Polarizable Continuum Model: Application to EPR Parameters
  and Paramagnetic NMR Shifts
  }
  \\
  Accepted for publication in \textit{Mol. Phys.}
\label{pcmepr}

\item
  \textbf{R. Di Remigio}, M. T. P. Beerepoot, Y. Cornaton, M. Ringholm,
  A. H. S. Steindal, K. Ruud, and L. Frediani
  \\
  \textsc{
  Open-ended formulation of self-consistent field response theory with
  the polarizable continuum model for solvation
  }
  \\
  In preparation for submission to \textit{Phys. Chem. Chem. Phys.}
\label{pcmopenrsp}
\end{enumerate}
